StateSpaceModels.jl: a Julia Package for Time-Series Analysis in a State-Space Framework

### 2020-02-25 paper/paper.tex
Add reference to repo

In this section, we present several practical applications which can be addressed via state-space modeling. We utilize \texttt{StateSpaceModels.jl} to tackle the presented problems and provide the results. Furthermore, for the sake of reproducibility, the code of some of the examples is in the folder \texttt{examples} in the \texttt{StateSpaceModels.jl} repository.

@@

We can also forecast the following two years of the time series by using the \texttt{forecast} function. The result is displayed in Fig. \ref{fig:log_airline_forecast}.
%
\begin{lstlisting}[language = Julia]
# Number of months ahead to be forecast
N = 24
# Perform forecasting
pred, dist = forecast(ss, N)
\end{lstlisting}
%
\begin{figure}[h]
	\centering
	\includegraphics[width=\columnwidth]{Figures/log_airline_forecast.pdf}
	\caption{Log-airline passengers historical data and forecasting.}
	\label{fig:log_airline_forecast}
\end{figure}
%
\begin{figure}[h]
	\centering
	\includegraphics[width=\columnwidth]{Figures/log_airline_components.pdf}
	\caption{Smoothed trend and seasonal components of the log-airline passengers time series.}
	\label{fig:log_airline_components}
\end{figure}

>>>>

In this section, we present several practical applications which can be addressed via state-space modeling. We utilize \texttt{StateSpaceModels.jl} to tackle the presented problems and provide the results. Furthermore, for the sake of reproducibility, the code of some of the examples is in the folder \texttt{examples} in the \texttt{StateSpaceModels.jl} repository \cite{statespacemodels}.

@@

We can also forecast the following two years of the time series by using the \texttt{forecast} function. The result is displayed in Fig. \ref{fig:log_airline_forecast}.
%
\begin{lstlisting}[language = Julia]
# Number of months ahead to be forecast
N = 24
# Perform forecasting
pred, dist = forecast(ss, N)
\end{lstlisting}
%
\begin{figure}[h]
	\centering
	\includegraphics[width=\columnwidth]{Figures/log_airline_forecast.pdf}
	\caption{Log-airline passengers historical data and forecast for the following two years.}
	\label{fig:log_airline_forecast}
\end{figure}
%
\begin{figure}[h]
	\centering
	\includegraphics[width=\columnwidth]{Figures/log_airline_components.pdf}
	\caption{Smoothed trend and seasonal components of the log-airline passengers time series.}
	\label{fig:log_airline_components}
\end{figure}
